\Title

### 2016-08-18 manuscript/manuscript.tex
Describe parecis and parnaiba

Differences between our Moho depth model and the seismological data
(shown in Fig.~\ref{fig:sam-residuals}b)
may indicate regions where our initial assumptions
(summarized in Fig.~\ref{fig:anomalysketch})
are inadequate or where we have
failed to correct for all crustal and mantle sources.
In general, our model fits both the seismological and gravity data well
in the oceans and in the Atlantic coast.
The largest differences are seen the along the Andean Province.
These differences are likely caused by the fact that our model does not include
the subducting Nazca plate.
Furthermore, the CRUST1.0 synthetic data test (Fig.~\ref{fig:crust1-results})
suggests that our inversion method is not able to fully recover deep Moho
depths in the Andes,
even without the effect of the subducting plate.

>>>>

Differences between our Moho depth model and the seismological data
(shown in Fig.~\ref{fig:sam-residuals}b)
may indicate regions where our initial assumptions
(summarized in Fig.~\ref{fig:anomalysketch})
are inadequate or where we have
failed to correct for all crustal and mantle sources.
The largest differences are seen the along the Andean Province.
These differences are likely caused by the fact that our model does not include
the subducting Nazca plate.
Furthermore, the CRUST1.0 synthetic data test (Fig.~\ref{fig:crust1-results})
suggests that our inversion method is not able to fully recover deep Moho
depths in the Andes,
even without the effect of the subducting plate.

In general, our model fits both the seismological and gravity data well
in the oceans and in the Atlantic coast.
The Parnaíba Basin has deep Moho surrounding its continental borders, following
inward with a shallower Moho, then a deeper step, and finally a shallower
part in the middle of the basin.
Our model has small differences with the few seismological data points that
fall inside and on the borders of the basin.
However, recent deep seismic reflection studies by \citet{daly2014} that cross
the basin in from west to east agree with our model.
Our model reveals a deep Moho in the Northern border of the Parecis Basin that
is corroborated by a single seismological data point.
